---
title: "Fitness evolution since october"
output: html_document
date: "2024-12-04"
---
# The first step is to setup the libraries
```{r load options, include=}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(scipen = 999)

# List of packages for session
.packages = c("here","doSNOW", "dplyr", "ggplot2", "tidyr")

# Load packages into session 
lapply(.packages, require, character.only=TRUE)

```

## R Markdown

Each calibration trial reduces the difference between observation and simulation. The difference is called "fitness. This is an exploration of the fitness improvement since october, when the weight-at-age were included in the robot calibration process. 
The files tracking the calibration trial are saved in the folder "keep_track_calibration".
We open them:

```{r pressure, echo=FALSE}

path <- here("psatlantismodel/Atlantis_Calibration/keep_track_calibration")
files <- list.files(path)
filtered_list <- files[grepl("\\.results$", files)]
calib_results <- c()
numbers <- as.numeric(sub("^([0-9]+).*", "\\1", filtered_list))
sorted_list <- filtered_list[order(numbers)]
for (file in sorted_list) {
  print(paste("Opening of:", file))
  a <- readRDS(paste(path, file, sep = "/"))
  print(a$trace$best)
  calib_results[[file]] <- a$trace$value
}




```

Now that we have retrieved the outputs of the calibration, we estimate a fitness value before each trial before the calibration and insert it in each trial vector 
```{r}
for (file in names(calib_results)) {
  # Récupérer le vecteur
  vec <- calib_results[[file]]
  
  # Calculer l'élément à ajouter
  new_element <- vec[1] + (vec[1] - vec[2])
  
  # Ajouter l'élément au début du vecteur
  calib_results[[file]] <- c(new_element, vec)
}
```

## Including Plots

You can also embed plots, for example:

```{r}
{par(mfrow = c(1,2))
plot(c(unlist(calib_results)[-(1:5)]), type = "l", 
     xlab = "Calibration generations", ylab = "Fitness", ylim = c(0,12000), main = "Total fitness")
plot(10^(c(unlist(calib_results)[-(1:5)]/447/2)^0.5), type = "l", 
     xlab = "Calibration generations", ylab = "Mean relative error", ylim = c(0,4300), main = "Mean relative error per target")}


```

Better plots in ggplot
```{r}

# Extract calibration results, removing the first 5 elements
fitness_values <- c(unlist(calib_results)[-(1:5)])
generations <- seq_along(fitness_values)

# Compute mean relative error
mean_relative_error <- 10^((fitness_values / 447 / 2)^0.5)

# Create a data frame
df <- data.frame(Generation = generations,
  Fitness = fitness_values,
  Mean_Relative_Error = mean_relative_error)

# Reshape for faceting
df_long <- df %>%
  pivot_longer(cols = c(Fitness, Mean_Relative_Error), names_to = "Metric", values_to = "Value")

# Define pretty labels
metric_labels <- c("Fitness" = "A.  Total Fitness", "Mean_Relative_Error" = "B.  Mean Relative Error per target")

# Create the plot
ggplot(df_long, aes(x = Generation, y = Value)) +
  geom_line(color = "steelblue", linewidth = 1) +
  facet_wrap(~ Metric, scales = "free_y", labeller = labeller(Metric = metric_labels)) +
  theme_minimal(base_size = 14) +
  labs(x = "Calibration Generations", y = NULL) +
  theme(
    strip.text = element_text(size = 12, face = "bold", hjust = 0),
    panel.grid.major = element_line(color = "gray95"),
    panel.grid.minor = element_blank()
  )
```



```{r}

```

