---
title: "Fitness evolution since october"
output: html_document
date: "2024-12-04"
---
# The first step is to setup the libraries
```{r load options, include=}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(scipen = 999)

# List of packages for session
.packages = c("here","doSNOW")

# Load packages into session 
lapply(.packages, require, character.only=TRUE)

```

## R Markdown

Each calibration trial reduces the difference between observation and simulation. The difference is called "fitness. This is an exploration of the fitness improvement since october, when the weight-at-age were included in the robot calibration process. 
The files tracking the calibration trial are saved in the folder "keep_track_calibration".
We open them:

```{r pressure, echo=FALSE}

path <- here("psatlantismodel/Atlantis_Calibration/keep_track_calibration")
files <- list.files(path)
filtered_list <- files[grepl("\\.results$", files)]
calib_results <- c()
numbers <- as.numeric(sub("^([0-9]+).*", "\\1", filtered_list))
sorted_list <- filtered_list[order(numbers)]
for (file in sorted_list) {
  print(paste("Opening of:", file))
  a <- readRDS(paste(path, file, sep = "/"))
  print(a$trace$best)
  calib_results[[file]] <- a$trace$value
}




```

Now that we have retrieved the outputs of the calibration, we estimate a fitness value before each trial before the calibration and insert it in each trial vector 
```{r}
for (file in names(calib_results)) {
  # Récupérer le vecteur
  vec <- calib_results[[file]]
  
  # Calculer l'élément à ajouter
  new_element <- vec[1] + (vec[1] - vec[2])
  
  # Ajouter l'élément au début du vecteur
  calib_results[[file]] <- c(new_element, vec)
}
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}

plot(c(unlist(calib_results)[-(1:5)]), type = "l", 
     xlab = "Calibration generations", ylab = "Fitness", ylim = c(0,12000))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
